On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-06 documents/paper.tex
Review of safety

\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{blindtext,graphicx}
\usepackage[absolute]{textpos}
\usepackage[parfill]{parskip}
\usepackage[colorlinks]{hyperref}
\usepackage{hyperref}
\usepackage{gensymb}
\usepackage{csquotes}

@@

\paragraph{\textbf{Time dependence}}\

@@

\clearpage
\begin{multicols}{1}
{\Large Biology}\\

@@

@@

{\Large Mass production}

\paragraph{Acknowledgements}\

This paper is not novel enough to deserve this chapter, but those to be acknowledged are.

@@

@@

>>>>

\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{blindtext,graphicx}
\usepackage[absolute]{textpos}
\usepackage[parfill]{parskip}
\usepackage[colorlinks]{hyperref}
\usepackage{hyperref}
\usepackage{gensymb}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{fontawesome}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{\textbf{Time dependence}}\

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
{\Large Safety}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations.

For instance, we could question why we might not see such resonances in bodily tissues. After all, approximately similar nanoscopic structures exist in humans; for instance, nuclear pores (120 nm) and the famous microtubules (10x50 nm).

While from which epidemiological data could be derived. \footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}

[ICNIRP 2020], [ICNIRP 2019], [Adair]

The existence of resonance modes in DNA has been a matter of some contention; but the best data demonstrates 
quite conclusively

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
 [Manikowska 1979] & 9.4 GHz pulsed &  \\ \hline
\end{tabular}
\end{center}

\begin{autem}
	{\it Evidence against safety}\

	\begin{itemize}
	  \item {[Manikowska 1979] / 9.4 GHz pulsed / 2 weeks\

	   this is a particularly concerning paper. [Servantie 1989] discusses the (somewhat }

	  \item {[Sagripanti 1986] find DNA damage at $8.5 mW/g$ at 2.55 GHz, without undue heating of the solvent.
	  	}

	\end{itemize}\

\end{autem}

\begin{toolchain}
	{\it Evidence for safety:}\
	\begin{itemize}
	  \item
 	\end{itemize}\
\end{toolchain}

{\it Please contact the author if you are aware of other salient research, or have a different interpretation.}

Adair, 2002:

The conclusion that there can be no microwave resonances in DNA in water is in accord with the results of measurements in three different laboratories ([Gabriel et al., 1987] [Foster et al., 1987] using techniques designed to detect resonances with amplitudes less than 1/20th of that reported by [Edwards et al. (1984)].

 Evidence of such microwave absorption resonances has been reported ([Edwards et al., 1984] [Grundler and Keilman, 1983], but these results have not been replicated ([Gabriel et al., 1987] [Foster et al., 1987]

> We extend analyses that suggest that the damping of the vibratory motion by biological fluids severely restrict such possibilities[].

It is interesting that this analysis would seem to disagree with the viral resonance seen by Yang.

[Foster (1987)] find that the DNA resonance found by [Edwards (1987)] was well below the experimental error, given the latter's setup. The Foster paper is of excellent quality.

 What is that in $mw/cm^2$?

Via the :

> This is typically described as a function of a relevant dosimetric quantity. For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass (W kg−1). Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area(W m−2), which we refer to as “absorbed power density”.
> 
> Similarly, as there is no evidence that continuous (e.g., sinusoidal) and discontinuous (e.g., pulsed) EMFs result in different biological effects (Kowalczuk et al. 2010; Juutilainen et al. 2011), no theoretical distinction has been made between these types of exposure (all exposures have been considered empirically in terms of whether they adversely affect health)

Juutilainen references a wealth of empirical data. Vijayalaxmi (2006) is particularly helpful:

Chemeris discusses 8.8 GHz  pulses, and finds no effect:

> We found no data on genotoxic effects of HPPP EMF at peak SAR exceeding hundreds of megawatts per kilogram and at average SAR, which does not induce dramatic overheating of the exposed objects. At such powerful EMF, peak electric field intensity in the exposed biological objects is close to maximally achievable, i.e. near breakdown electric field intensity. It would be reasonable to expect specific genotoxic effects of RF EMF under such extreme conditions.

\footnote{``{\it{For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$. Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}}'' [ICNIRP 2020 \faExternalLink]}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
{\Large Biology}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
{\Large Modes of application}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{\textbf{Personal 'electromagnetic mask'}}\

We demonstrate this form factor because, superficially, there are fewer people than there are places. Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.

On the other hand, a personal device may present issues with compliance\footnote{that sounds evil, but it really isn't} and production volume.

\paragraph{\textbf{Direct treatments}}\

[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth of 10 GHz microwave is approximately:

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
F=10 GHz          & Dry tissue & Wet tissue \\ \hline
Penetration depth & 30 mm      & $\sim$5 mm \\ \hline
\end{tabular}
\end{center}

SARS is found widely distributed throughout the most desirable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.

However, destruction of lung tissue appears to be the 	[Yuan 2019]

\paragraph{\textbf{More fanciful concepts}}\

Many weather radar systems operate in these X-band frequency ranges.

It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Large Mass production}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If this 'electromagnetic mask' form is the ideal (not nearly ), a minimum of 5 GaAs or SiGe:C transistors will be required.

There are, for instance, 1 million hospital beds in the U.S. [AHA 2018].

It is difficult to determine the supply capacity for these modern semiconductor processes. A few fermi est

GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices =

3e9 wifi connected devices produced each year.

The largest RFID plants can produce

The techniques and equipment required to produce these are non-trivial. SiGe:C, for instance, requires,

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This paper is not novel enough to deserve this chapter, but those to be acknowledged are.

@@

NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc. "matrix not positive definite". [Schutt-Aine] discusses this; we reproduce here for convienience.

\[ L_{11} = L_{22} = L_{even}  \]
\[ L_{12} = L_{21} = L_{odd}  \]
\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]

@@

Sacred, recipy, Sumatra
